Supporting Information

### 2018-03-06 SupportingInformation.Rmd
finished adding narative for soil CN nonparametric tail dependence stuff, running now

As described in Methods, each of our statistics, as computed for the 
ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$, was compared to the distributions 
of values of the same statistic (with the same ranges) on 1000 normal-copula 
surrogate datasets with similar Kendall or Spearman correlations, in different 
runs (`r fig_nums("soilCN_nonparam",display="c")`). Because the correlation 
used in the Cor statistic is the Spearman correlation, Spearman-preserving surrogates
should be used, so the top-left panel of `r fig_nums("soilCN_nonparam",display="c")`
should be ignored (DAN: need to fix this). Results indicate
DAN: continue here.

@@

<!--Now make a table, this one about asymmetry of tail dependence-->
```{r plot_soilCN_asymmtry_taildep, echo=F}
atdres<-data.frame(Statistic=c("Corl-Coru","Pl-Pu","D2u-D2l"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
fractxt<-function(fracval)
{
  ptxt<-''
  if (fracval>.975*numsurrog)
  {
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<.025*numsurrog)
  {
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}
atdres[1,2]<-fractxt(corlmcoru_frac_K)
atdres[1,3]<-fractxt(corlmcoru_frac_S)
atdres[2,2]<-fractxt(PlmPu_frac_K)
atdres[2,3]<-fractxt(PlmPu_frac_S)
atdres[3,2]<-fractxt(D2umD2l_frac_K)
atdres[3,3]<-fractxt(D2umD2l_frac_S)
atdres
```

>>>>

As described in Methods, each of our statistics, as computed for the 
ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$, was compared to the distributions 
of values of the same statistic with the same ranges computed on 1000 normal-copula 
surrogate datasets with similar Kendall or Spearman correlations, in different 
runs (`r fig_nums("soilCN_nonparam",display="c")`). Because the correlation 
used in the Cor statistic is the Spearman correlation, Spearman-preserving surrogates
should be used, so the top-left panel of `r fig_nums("soilCN_nonparam",display="c")`
should be ignored (DAN: need to fix this later). Results indicate that tail dependence of 
data is stronger in both the lower and upper tails than would be expected under a 
null hypothesis of a normal copula. The dependence between C and N is also 
weaker in the middle of both marginal distributions
than would be expected based on a normal-copula null model.

@@

We also tested statistically for asymmetry of tail dependence, which seems visible in `r table_nums("soilCNcop",display="c")`. 
Results (`r table_nums("soilCN_asym",display="c")`) show that upper-tail dependence was, indeed, significantly stronger than lower-tail dependence in these data.

<!--Now make and display a table, this one about asymmetry of tail dependence-->
```{r plot_soilCN_asymmtry_taildep, echo=F}
atdres<-data.frame(Statistic=c("Corl-Coru","Pl-Pu","D2u-D2l"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
fractxt<-function(fracval)
{
  ptxt<-''
  if (fracval>.5*numsurrog)
  {
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog)
  {
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}
atdres[1,2]<-fractxt(corlmcoru_frac_K)
atdres[1,3]<-fractxt(corlmcoru_frac_S)
atdres[2,2]<-fractxt(PlmPu_frac_K)
atdres[2,3]<-fractxt(PlmPu_frac_S)
atdres[3,2]<-fractxt(D2umD2l_frac_K)
atdres[3,3]<-fractxt(D2umD2l_frac_S)

table_nums("soilCN_asym",display=F)
knitr::kable(atdres, caption = "Results for tests of whether asymmetry of tail dependence is significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the ranges $0-0.1$ and $0.9-1$ (Methods). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates.")
```
